Atlantis to SS for California Current sardines and hake: full fishing and

### 2020-01-13 Sardines_atlantisom2SS_demo.Rmd
demo used at NEMOW commenting out one hardcode file path

```{r message=FALSE, warning=FALSE}
library(tidyr)
require(dplyr)
library(ggplot2)
library(data.table)
library(here)
library(ggforce)
library(ggthemes)
#For testing
devtools::load_all("C:/Users/chris/Documents/GitHub/atlantisom")
library(atlantisom)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(tidyr)
require(dplyr)
library(ggplot2)
library(data.table)
library(here)
library(ggforce)
library(ggthemes)
#For testing
#devtools::load_all("C:/Users/chris/Documents/GitHub/atlantisom")
library(atlantisom)
```
